---
title: "Comprehensive Behavioral Analysis - All Paradigms"
author: "DLCAnalyzer Pipeline"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    code_folding: hide
    theme: flatly
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 10,
  fig.height = 8,
  dpi = 300
)

# Ensure we're in the correct working directory
# When knitting, this should already be the directory containing the .Rmd file
if (!file.exists("R/core/data_loading.R")) {
  stop("Working directory is incorrect. Expected to be in DLCAnalyzer root directory. Current: ", getwd())
}

# Set output directory
output_dir <- "output/comprehensive_analysis"
dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
```

# Overview

This document provides a comprehensive analysis of all behavioral paradigm data in the DLCAnalyzer repository:

- **LD (Light/Dark Box)**: Anxiety assessment
- **OFT (Open Field Test)**: Exploration and anxiety
- **NORT (Novel Object Recognition Test)**: Memory and recognition
- **EPM (Elevated Plus Maze)**: Anxiety and risk assessment

---

# Setup and Dependencies

```{r load-libraries}
# Load required packages
suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
  library(tidyr)
  library(knitr)
  library(readxl)
})

# Suppress verbose readxl messages
options(readxl.verbose = FALSE)

# Source all DLCAnalyzer functions
suppressMessages({
  source("R/core/data_loading.R")
  source("R/core/preprocessing.R")
  source("R/core/coordinate_transforms.R")
  source("R/core/data_structures.R")
  source("R/core/arena_config.R")
  source("R/core/quality_checks.R")

  # Paradigm-specific functions
  source("R/ld/ld_load.R")
  source("R/ld/ld_analysis.R")
  source("R/ld/ld_report.R")

  source("R/oft/oft_load.R")
  source("R/oft/oft_analysis.R")
  source("R/oft/oft_report.R")

  source("R/nort/nort_load.R")
  source("R/nort/nort_analysis.R")
  source("R/nort/nort_report.R")

  source("R/epm/epm_load.R")
  source("R/epm/epm_analysis.R")
  source("R/epm/epm_report.R")

  # Common utilities
  source("R/common/io.R")
  source("R/common/plotting.R")
  source("R/common/geometry.R")
  source("R/core/zone_geometry.R")
})

cat("✓ All functions loaded successfully\n")
```

---

# 1. Light/Dark Box (LD) Analysis

```{r ld-setup}
ld_data_dir <- "data/LD"
ld_sessions <- list.dirs(ld_data_dir, recursive = FALSE, full.names = TRUE)
cat("Found", length(ld_sessions), "LD session folders\n")
```

## 1.1 Load LD Data

```{r ld-load}
ld_all_data <- list()
ld_errors <- list()

for (session_dir in ld_sessions) {
  session_name <- basename(session_dir)
  cat("\nProcessing LD session:", session_name, "\n")

  # Find Excel files in this session
  excel_files <- list.files(session_dir, pattern = "\\.xlsx$",
                            full.names = TRUE, recursive = FALSE)

  for (file in excel_files) {
    trial_name <- tools::file_path_sans_ext(basename(file))
    cat("  Loading:", trial_name, "...")

    tryCatch({
      # Load LD data (suppress verbose Excel reading messages)
      data <- suppressMessages(load_ld_data(file, fps = 25))

      # Store by session and trial
      if (!session_name %in% names(ld_all_data)) {
        ld_all_data[[session_name]] <- list()
      }
      ld_all_data[[session_name]][[trial_name]] <- data
      cat(" ✓\n")

    }, error = function(e) {
      cat(" ✗ ERROR:", e$message, "\n")
      ld_errors[[paste(session_name, trial_name, sep = "_")]] <- e$message
    })
  }
}

cat("\n✓ Loaded", sum(sapply(ld_all_data, length)), "LD trials\n")
if (length(ld_errors) > 0) {
  cat("✗ Errors in", length(ld_errors), "trials\n")
}
```

## 1.2 Analyze LD Data

```{r ld-analyze}
ld_results <- list()

for (session_name in names(ld_all_data)) {
  session_data <- ld_all_data[[session_name]]

  for (trial_name in names(session_data)) {
    trial_data <- session_data[[trial_name]]

    # Analyze each animal
    for (animal_name in names(trial_data)) {
      animal_data <- trial_data[[animal_name]]

      tryCatch({
        results <- analyze_ld(animal_data$data, fps = 25)

        # Store results with full identifier
        result_id <- paste(session_name, trial_name, animal_name, sep = "_")
        ld_results[[result_id]] <- c(
          session = session_name,
          trial = trial_name,
          animal_id = animal_name,
          arena_id = animal_data$arena_id,
          results
        )

      }, error = function(e) {
        cat("Error analyzing", animal_name, ":", e$message, "\n")
      })
    }
  }
}

# Convert to data frame
ld_results_df <- do.call(rbind, lapply(ld_results, as.data.frame))
ld_results_df <- ld_results_df %>%
  mutate(across(where(is.list), as.character))

cat("✓ Analyzed", nrow(ld_results_df), "LD animals\n")
```

## 1.3 LD Summary Statistics

```{r ld-summary}
if (nrow(ld_results_df) > 0) {
  ld_summary <- ld_results_df %>%
    summarise(
      n_subjects = n(),
      mean_time_light = mean(as.numeric(time_in_light_sec), na.rm = TRUE),
      mean_time_dark = mean(as.numeric(time_in_dark_sec), na.rm = TRUE),
      mean_entries_light = mean(as.numeric(entries_to_light), na.rm = TRUE),
      mean_latency_light = mean(as.numeric(latency_to_light_sec), na.rm = TRUE),
      mean_distance = mean(as.numeric(total_distance_cm), na.rm = TRUE)
    )

  kable(ld_summary, caption = "LD Summary Statistics", digits = 2)
}
```

## 1.4 LD Visualizations

```{r ld-plots, fig.height=6}
if (nrow(ld_results_df) > 0) {
  # Time in light vs dark
  p1 <- ggplot(ld_results_df, aes(x = animal_id)) +
    geom_col(aes(y = as.numeric(time_in_light_sec), fill = "Light"),
             position = "dodge", alpha = 0.7) +
    geom_col(aes(y = as.numeric(time_in_dark_sec), fill = "Dark"),
             position = "dodge", alpha = 0.7) +
    scale_fill_manual(values = c("Light" = "#FFD700", "Dark" = "#2C3E50")) +
    labs(title = "LD: Time in Light vs Dark Zones",
         x = "Animal ID", y = "Time (seconds)", fill = "Zone") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  print(p1)

  # Anxiety ratio (time in light / total time)
  ld_results_df$anxiety_ratio <- as.numeric(ld_results_df$time_in_light_sec) /
    (as.numeric(ld_results_df$time_in_light_sec) + as.numeric(ld_results_df$time_in_dark_sec))

  p2 <- ggplot(ld_results_df, aes(x = session, y = anxiety_ratio, fill = session)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.5) +
    labs(title = "LD: Anxiety Ratio by Session",
         subtitle = "Higher ratio = more time in light = lower anxiety",
         x = "Session", y = "Light Time Ratio") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

  print(p2)
}
```

## 1.5 Export LD Results

```{r ld-export}
if (nrow(ld_results_df) > 0) {
  ld_output_file <- file.path(output_dir, "LD_all_results.csv")
  write.csv(ld_results_df, ld_output_file, row.names = FALSE)
  cat("✓ Exported LD results to:", ld_output_file, "\n")
}
```

---

# 2. Open Field Test (OFT) Analysis

```{r oft-setup}
oft_data_dir <- "data/OFT"
oft_sessions <- list.dirs(oft_data_dir, recursive = FALSE, full.names = TRUE)
cat("Found", length(oft_sessions), "OFT session folders\n")
```

## 2.1 Load OFT Data

```{r oft-load}
oft_all_data <- list()
oft_errors <- list()

for (session_dir in oft_sessions) {
  session_name <- basename(session_dir)
  cat("\nProcessing OFT session:", session_name, "\n")

  excel_files <- list.files(session_dir, pattern = "\\.xlsx$",
                            full.names = TRUE, recursive = FALSE)

  for (file in excel_files) {
    trial_name <- tools::file_path_sans_ext(basename(file))
    cat("  Loading:", trial_name, "...")

    tryCatch({
      data <- suppressMessages(load_oft_data(file, fps = 25))

      if (!session_name %in% names(oft_all_data)) {
        oft_all_data[[session_name]] <- list()
      }
      oft_all_data[[session_name]][[trial_name]] <- data
      cat(" ✓\n")

    }, error = function(e) {
      cat(" ✗ ERROR:", e$message, "\n")
      oft_errors[[paste(session_name, trial_name, sep = "_")]] <- e$message
    })
  }
}

cat("\n✓ Loaded", sum(sapply(oft_all_data, length)), "OFT trials\n")
if (length(oft_errors) > 0) {
  cat("✗ Errors in", length(oft_errors), "trials\n")
}
```

## 2.2 Analyze OFT Data

```{r oft-analyze}
oft_results <- list()

for (session_name in names(oft_all_data)) {
  session_data <- oft_all_data[[session_name]]

  for (trial_name in names(session_data)) {
    trial_data <- session_data[[trial_name]]

    for (animal_name in names(trial_data)) {
      animal_data <- trial_data[[animal_name]]

      tryCatch({
        results <- analyze_oft(animal_data$data, fps = 25)

        result_id <- paste(session_name, trial_name, animal_name, sep = "_")
        oft_results[[result_id]] <- c(
          session = session_name,
          trial = trial_name,
          animal_id = animal_name,
          arena_id = animal_data$arena_id,
          results
        )

      }, error = function(e) {
        cat("Error analyzing", animal_name, ":", e$message, "\n")
      })
    }
  }
}

oft_results_df <- do.call(rbind, lapply(oft_results, as.data.frame))
oft_results_df <- oft_results_df %>%
  mutate(across(where(is.list), as.character))

cat("✓ Analyzed", nrow(oft_results_df), "OFT animals\n")
```

## 2.3 OFT Summary Statistics

```{r oft-summary}
if (nrow(oft_results_df) > 0) {
  oft_summary <- oft_results_df %>%
    summarise(
      n_subjects = n(),
      mean_time_center = mean(as.numeric(time_in_center_sec), na.rm = TRUE),
      mean_pct_center = mean(as.numeric(pct_time_in_center), na.rm = TRUE),
      mean_entries_center = mean(as.numeric(entries_to_center), na.rm = TRUE),
      mean_thigmotaxis = mean(as.numeric(thigmotaxis_index), na.rm = TRUE),
      mean_distance = mean(as.numeric(total_distance_cm), na.rm = TRUE)
    )

  kable(oft_summary, caption = "OFT Summary Statistics", digits = 2)
}
```

## 2.4 OFT Visualizations

```{r oft-plots, fig.height=6}
if (nrow(oft_results_df) > 0) {
  # Center time comparison
  p1 <- ggplot(oft_results_df, aes(x = animal_id, y = as.numeric(pct_time_in_center), fill = session)) +
    geom_col(position = "dodge") +
    labs(title = "OFT: Percentage Time in Center",
         subtitle = "Lower time = higher anxiety",
         x = "Animal ID", y = "Time in Center (%)") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))

  print(p1)

  # Thigmotaxis index
  p2 <- ggplot(oft_results_df, aes(x = session, y = as.numeric(thigmotaxis_index), fill = session)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.5) +
    labs(title = "OFT: Thigmotaxis Index by Session",
         subtitle = "Higher index = more wall-hugging = higher anxiety",
         x = "Session", y = "Thigmotaxis Index") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

  print(p2)
}
```

## 2.5 Export OFT Results

```{r oft-export}
if (nrow(oft_results_df) > 0) {
  oft_output_file <- file.path(output_dir, "OFT_all_results.csv")
  write.csv(oft_results_df, oft_output_file, row.names = FALSE)
  cat("✓ Exported OFT results to:", oft_output_file, "\n")
}
```

---

# 3. Novel Object Recognition Test (NORT) Analysis

```{r nort-setup}
nort_data_dir <- "data/NORT"
nort_sessions <- list.dirs(nort_data_dir, recursive = FALSE, full.names = TRUE)
cat("Found", length(nort_sessions), "NORT session folders\n")
```

## 3.1 Load NORT Data

```{r nort-load}
nort_all_data <- list()
nort_errors <- list()

for (session_dir in nort_sessions) {
  session_name <- basename(session_dir)
  cat("\nProcessing NORT session:", session_name, "\n")

  # Determine session type from directory name
  # D1 and D2 (or "hab") = habituation (no novel object)
  # D3 = test phase (novel object present)
  is_habituation <- grepl("hab|D1|D2", session_name, ignore.case = TRUE) &&
                    !grepl("D3", session_name)
  novel_side <- if (is_habituation) "neither" else "left"  # Default to "left" for test phase

  cat("  Session type:", if (is_habituation) "Habituation" else "Test",
      "| Novel side:", novel_side, "\n")

  excel_files <- list.files(session_dir, pattern = "\\.xlsx$",
                            full.names = TRUE, recursive = FALSE)
  # Exclude temporary Excel files
  excel_files <- excel_files[!grepl("^~\\$", basename(excel_files))]

  for (file in excel_files) {
    trial_name <- tools::file_path_sans_ext(basename(file))
    cat("  Loading:", trial_name, "...")

    tryCatch({
      data <- suppressMessages(load_nort_data(file, fps = 25, novel_side = novel_side))

      if (!session_name %in% names(nort_all_data)) {
        nort_all_data[[session_name]] <- list()
      }
      nort_all_data[[session_name]][[trial_name]] <- data
      cat(" ✓\n")

    }, error = function(e) {
      cat(" ✗ ERROR:", e$message, "\n")
      nort_errors[[paste(session_name, trial_name, sep = "_")]] <- e$message
    })
  }
}

cat("\n✓ Loaded", sum(sapply(nort_all_data, length)), "NORT trials\n")
if (length(nort_errors) > 0) {
  cat("✗ Errors in", length(nort_errors), "trials\n")
}
```

## 3.2 Analyze NORT Data

```{r nort-analyze}
nort_results <- list()

for (session_name in names(nort_all_data)) {
  session_data <- nort_all_data[[session_name]]

  for (trial_name in names(session_data)) {
    trial_data <- session_data[[trial_name]]

    for (animal_name in names(trial_data)) {
      animal_data <- trial_data[[animal_name]]

      tryCatch({
        # Get novel_side from animal_data (set during loading)
        novel_side <- animal_data$novel_side
        if (is.null(novel_side)) novel_side <- "left"

        # Only analyze if test phase (novel_side is not "neither")
        if (novel_side != "neither") {
          results <- analyze_nort(animal_data$data, fps = 25, novel_side = novel_side)

          result_id <- paste(session_name, trial_name, animal_name, sep = "_")
          nort_results[[result_id]] <- c(
            session = session_name,
            trial = trial_name,
            animal_id = animal_name,
            arena_id = animal_data$arena_id,
            results
          )
        } else {
          cat("Skipping habituation phase for", animal_name, "\n")
        }

      }, error = function(e) {
        cat("Error analyzing", animal_name, ":", e$message, "\n")
      })
    }
  }
}

nort_results_df <- do.call(rbind, lapply(nort_results, as.data.frame))
nort_results_df <- nort_results_df %>%
  mutate(across(where(is.list), as.character))

cat("✓ Analyzed", nrow(nort_results_df), "NORT animals\n")
```

## 3.3 NORT Summary Statistics

```{r nort-summary}
if (nrow(nort_results_df) > 0) {
  nort_summary <- nort_results_df %>%
    summarise(
      n_subjects = n(),
      mean_DI = mean(as.numeric(discrimination_index), na.rm = TRUE),
      mean_pref_score = mean(as.numeric(preference_score), na.rm = TRUE),
      mean_novel_time = mean(as.numeric(novel_object_time_sec), na.rm = TRUE),
      mean_familiar_time = mean(as.numeric(familiar_object_time_sec), na.rm = TRUE),
      mean_total_exploration = mean(as.numeric(total_exploration_sec), na.rm = TRUE),
      pct_valid_trials = sum(as.logical(is_valid_trial), na.rm = TRUE) / n() * 100
    )

  kable(nort_summary, caption = "NORT Summary Statistics", digits = 3)
}
```

## 3.4 NORT Visualizations

```{r nort-plots, fig.height=6}
if (nrow(nort_results_df) > 0) {
  # Discrimination Index
  p1 <- ggplot(nort_results_df, aes(x = session, y = as.numeric(discrimination_index), fill = session)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.5) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red") +
    labs(title = "NORT: Discrimination Index by Session",
         subtitle = "DI > 0: novel preference | DI < 0: familiar preference",
         x = "Session", y = "Discrimination Index") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

  print(p1)

  # Novel vs Familiar exploration time
  nort_long <- nort_results_df %>%
    select(animal_id, session, novel_object_time_sec, familiar_object_time_sec) %>%
    pivot_longer(cols = c(novel_object_time_sec, familiar_object_time_sec),
                 names_to = "object_type", values_to = "time") %>%
    mutate(time = as.numeric(time),
           object_type = ifelse(grepl("novel", object_type), "Novel", "Familiar"))

  p2 <- ggplot(nort_long, aes(x = object_type, y = time, fill = object_type)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.3) +
    scale_fill_manual(values = c("Novel" = "#E74C3C", "Familiar" = "#3498DB")) +
    labs(title = "NORT: Object Exploration Time",
         x = "Object Type", y = "Exploration Time (seconds)") +
    theme_minimal() +
    theme(legend.position = "none")

  print(p2)
}
```

## 3.5 Export NORT Results

```{r nort-export}
if (nrow(nort_results_df) > 0) {
  nort_output_file <- file.path(output_dir, "NORT_all_results.csv")
  write.csv(nort_results_df, nort_output_file, row.names = FALSE)
  cat("✓ Exported NORT results to:", nort_output_file, "\n")
}
```

---

# 4. Elevated Plus Maze (EPM) Analysis

```{r epm-setup}
epm_data_dir <- "data/EPM/Example DLC Data"
epm_sessions <- list.dirs(epm_data_dir, recursive = FALSE, full.names = TRUE)
cat("Found", length(epm_sessions), "EPM session folders\n")
```

## 4.1 Load EPM Data

```{r epm-load}
epm_all_data <- list()
epm_errors <- list()

for (session_dir in epm_sessions) {
  session_name <- basename(session_dir)
  cat("\nProcessing EPM session:", session_name, "\n")

  csv_files <- list.files(session_dir, pattern = "\\.csv$",
                          full.names = TRUE, recursive = FALSE)
  # Exclude filtered files
  csv_files <- csv_files[!grepl("_filtered\\.csv$", csv_files)]

  for (file in csv_files) {
    subject_id <- gsub("_superanimal.*", "", basename(file))
    cat("  Loading:", subject_id, "...")

    tryCatch({
      # Load EPM data with default parameters
      # NOTE: Adjust pixels_per_cm if calibration is known
      data <- suppressMessages(load_epm_data(file, fps = 25, pixels_per_cm = 5.3,
                                             body_part = "mouse_center"))

      if (!session_name %in% names(epm_all_data)) {
        epm_all_data[[session_name]] <- list()
      }
      epm_all_data[[session_name]][[subject_id]] <- data
      cat(" ✓\n")

    }, error = function(e) {
      cat(" ✗ ERROR:", e$message, "\n")
      epm_errors[[paste(session_name, subject_id, sep = "_")]] <- e$message
    })
  }
}

cat("\n✓ Loaded", sum(sapply(epm_all_data, length)), "EPM subjects\n")
if (length(epm_errors) > 0) {
  cat("✗ Errors in", length(epm_errors), "subjects\n")
}
```

## 4.2 Analyze EPM Data

```{r epm-analyze}
epm_results <- list()

for (session_name in names(epm_all_data)) {
  session_data <- epm_all_data[[session_name]]

  for (subject_id in names(session_data)) {
    subject_data <- session_data[[subject_id]]

    tryCatch({
      results <- analyze_epm(subject_data, fps = 25)

      result_id <- paste(session_name, subject_id, sep = "_")
      epm_results[[result_id]] <- c(
        session = session_name,
        subject = subject_id,
        results
      )

    }, error = function(e) {
      cat("Error analyzing", subject_id, ":", e$message, "\n")
    })
  }
}

epm_results_df <- do.call(rbind, lapply(epm_results, as.data.frame))
epm_results_df <- epm_results_df %>%
  mutate(across(where(is.list), as.character))

cat("✓ Analyzed", nrow(epm_results_df), "EPM subjects\n")
```

## 4.3 EPM Summary Statistics

```{r epm-summary}
if (nrow(epm_results_df) > 0) {
  epm_summary <- epm_results_df %>%
    summarise(
      n_subjects = n(),
      mean_open_arm_ratio = mean(as.numeric(open_arm_ratio), na.rm = TRUE),
      mean_entries_ratio = mean(as.numeric(entries_ratio), na.rm = TRUE),
      mean_time_open = mean(as.numeric(time_in_open_arms_sec), na.rm = TRUE),
      mean_time_closed = mean(as.numeric(time_in_closed_arms_sec), na.rm = TRUE),
      mean_total_entries = mean(as.numeric(total_arm_entries), na.rm = TRUE),
      mean_distance = mean(as.numeric(total_distance_cm), na.rm = TRUE)
    )

  kable(epm_summary, caption = "EPM Summary Statistics", digits = 3)
}
```

## 4.4 EPM Visualizations

```{r epm-plots, fig.height=6}
if (nrow(epm_results_df) > 0) {
  # Open Arm Ratio (primary anxiety index)
  p1 <- ggplot(epm_results_df, aes(x = session, y = as.numeric(open_arm_ratio), fill = session)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.5) +
    geom_hline(yintercept = c(0.15, 0.25, 0.40, 0.55),
               linetype = "dashed", alpha = 0.3) +
    labs(title = "EPM: Open Arm Ratio by Session",
         subtitle = "Lower ratio = higher anxiety | Guidelines: <0.15 (high), 0.25-0.40 (moderate), >0.55 (low)",
         x = "Session", y = "Open Arm Ratio") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

  print(p1)

  # Time in arm types
  epm_long <- epm_results_df %>%
    select(subject, session, time_in_open_arms_sec, time_in_closed_arms_sec, time_in_center_sec) %>%
    pivot_longer(cols = c(time_in_open_arms_sec, time_in_closed_arms_sec, time_in_center_sec),
                 names_to = "zone", values_to = "time") %>%
    mutate(time = as.numeric(time),
           zone = case_when(
             grepl("open", zone) ~ "Open Arms",
             grepl("closed", zone) ~ "Closed Arms",
             grepl("center", zone) ~ "Center"
           ))

  p2 <- ggplot(epm_long, aes(x = zone, y = time, fill = zone)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.3) +
    scale_fill_manual(values = c("Open Arms" = "#E74C3C",
                                  "Closed Arms" = "#3498DB",
                                  "Center" = "#2ECC71")) +
    labs(title = "EPM: Time in Different Zones",
         x = "Zone", y = "Time (seconds)") +
    theme_minimal() +
    theme(legend.position = "none")

  print(p2)
}
```

## 4.5 Export EPM Results

```{r epm-export}
if (nrow(epm_results_df) > 0) {
  epm_output_file <- file.path(output_dir, "EPM_all_results.csv")
  write.csv(epm_results_df, epm_output_file, row.names = FALSE)
  cat("✓ Exported EPM results to:", epm_output_file, "\n")
}
```

---

# 5. Cross-Paradigm Comparisons

## 5.1 Sample Sizes

```{r cross-sample-sizes}
sample_sizes <- data.frame(
  Paradigm = c("LD", "OFT", "NORT", "EPM"),
  N_Subjects = c(
    ifelse(exists("ld_results_df"), nrow(ld_results_df), 0),
    ifelse(exists("oft_results_df"), nrow(oft_results_df), 0),
    ifelse(exists("nort_results_df"), nrow(nort_results_df), 0),
    ifelse(exists("epm_results_df"), nrow(epm_results_df), 0)
  )
)

ggplot(sample_sizes, aes(x = Paradigm, y = N_Subjects, fill = Paradigm)) +
  geom_col() +
  geom_text(aes(label = N_Subjects), vjust = -0.5) +
  labs(title = "Sample Sizes Across Paradigms",
       x = "Paradigm", y = "Number of Subjects/Arenas") +
  theme_minimal() +
  theme(legend.position = "none")
```

## 5.2 Anxiety Indices Comparison

```{r cross-anxiety}
# Compile anxiety-related metrics
anxiety_data <- data.frame(
  paradigm = character(),
  subject = character(),
  anxiety_index = numeric(),
  stringsAsFactors = FALSE
)

# LD: higher time in light = lower anxiety
if (exists("ld_results_df") && nrow(ld_results_df) > 0) {
  ld_anxiety <- data.frame(
    paradigm = "LD",
    subject = ld_results_df$animal_id,
    anxiety_index = as.numeric(ld_results_df$time_in_light_sec) /
      (as.numeric(ld_results_df$time_in_light_sec) + as.numeric(ld_results_df$time_in_dark_sec))
  )
  anxiety_data <- rbind(anxiety_data, ld_anxiety)
}

# OFT: higher time in center = lower anxiety (normalized)
if (exists("oft_results_df") && nrow(oft_results_df) > 0) {
  oft_anxiety <- data.frame(
    paradigm = "OFT",
    subject = oft_results_df$animal_id,
    anxiety_index = as.numeric(oft_results_df$pct_time_in_center) / 100
  )
  anxiety_data <- rbind(anxiety_data, oft_anxiety)
}

# EPM: open arm ratio (already 0-1)
if (exists("epm_results_df") && nrow(epm_results_df) > 0) {
  epm_anxiety <- data.frame(
    paradigm = "EPM",
    subject = epm_results_df$subject,
    anxiety_index = as.numeric(epm_results_df$open_arm_ratio)
  )
  anxiety_data <- rbind(anxiety_data, epm_anxiety)
}

if (nrow(anxiety_data) > 0) {
  ggplot(anxiety_data, aes(x = paradigm, y = anxiety_index, fill = paradigm)) +
    geom_boxplot() +
    geom_jitter(width = 0.2, alpha = 0.3) +
    labs(title = "Anxiety Indices Across Paradigms",
         subtitle = "Normalized: Higher = Lower Anxiety",
         x = "Paradigm", y = "Anxiety Index (normalized)") +
    theme_minimal() +
    theme(legend.position = "none")
}
```

---

# 6. Individual Animal Plots

## 6.1 Generate Individual EPM Plots

```{r individual-epm-plots, results='hide'}
if (length(epm_all_data) > 0) {
  epm_plots_dir <- file.path(output_dir, "EPM_individual_plots")
  dir.create(epm_plots_dir, recursive = TRUE, showWarnings = FALSE)

  for (session_name in names(epm_all_data)) {
    session_data <- epm_all_data[[session_name]]

    for (subject_id in names(session_data)) {
      subject_data <- session_data[[subject_id]]

      tryCatch({
        # Generate report for this subject
        subject_dir <- file.path(epm_plots_dir, session_name, subject_id)
        generate_epm_report(subject_data, output_dir = subject_dir, subject_id = subject_id)

      }, error = function(e) {
        cat("Error generating plots for", subject_id, ":", e$message, "\n")
      })
    }
  }

  cat("✓ Generated EPM plots in:", epm_plots_dir, "\n")
}
```

## 6.2 Generate Individual LD Plots

```{r individual-ld-plots, results='hide'}
if (length(ld_all_data) > 0) {
  ld_plots_dir <- file.path(output_dir, "LD_individual_plots")
  dir.create(ld_plots_dir, recursive = TRUE, showWarnings = FALSE)

  for (session_name in names(ld_all_data)) {
    session_data <- ld_all_data[[session_name]]

    for (trial_name in names(session_data)) {
      trial_data <- session_data[[trial_name]]

      for (animal_name in names(trial_data)) {
        animal_data <- trial_data[[animal_name]]

        tryCatch({
          subject_id <- paste(session_name, trial_name, animal_name, sep = "_")
          subject_dir <- file.path(ld_plots_dir, session_name, trial_name, animal_name)
          generate_ld_report(animal_data, output_dir = subject_dir, subject_id = subject_id)

        }, error = function(e) {
          cat("Error generating plots for", animal_name, ":", e$message, "\n")
        })
      }
    }
  }

  cat("✓ Generated LD plots in:", ld_plots_dir, "\n")
}
```

---

# 7. Summary

```{r final-summary}
cat("\n========================================\n")
cat("  Comprehensive Analysis Complete\n")
cat("========================================\n\n")

cat("Paradigms Analyzed:\n")
if (exists("ld_results_df")) cat("  ✓ LD:", nrow(ld_results_df), "animals\n")
if (exists("oft_results_df")) cat("  ✓ OFT:", nrow(oft_results_df), "animals\n")
if (exists("nort_results_df")) cat("  ✓ NORT:", nrow(nort_results_df), "animals\n")
if (exists("epm_results_df")) cat("  ✓ EPM:", nrow(epm_results_df), "animals\n")

cat("\nOutput Files:\n")
cat("  📊 Combined results CSV files in:", output_dir, "\n")
cat("  📈 Individual plots in:", output_dir, "/{paradigm}_individual_plots/\n")
cat("  📄 This HTML report\n")

cat("\nNext Steps:\n")
cat("  1. Review quality control metrics\n")
cat("  2. Verify novel side specification for NORT\n")
cat("  3. Adjust EPM pixels_per_cm calibration if needed\n")
cat("  4. Perform statistical comparisons between groups\n")
cat("  5. Generate publication-ready figures\n\n")
```

---

# Session Info

```{r session-info}
sessionInfo()
```
